Think deep for reef resilience

### 2025-08-07 paper/paper_draft.qmd
Formatting
For TI to flesh out
Slight tweak to discussion intro

: Table 1: Information for each GCM used in this investigation including ECS value,
interpreted relative severity and where results are individual GCM results are displayed. GCMs in context with assessed plausible ranges of ECS values are displayed in [@sfig-ecs].
ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS values, thus
results are displayed in the main text. ECS value sources: .

@@

@@

Under all GCMs most reefs are projected to suffer substantial declines in coral cover from
2025 levels. NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover maintanance into
the future. Differences between low, medium and high reef clusters in cover timeseries are
most notable under these two GCMs. Maintainance of coral cover into the future is not
clearly linked to the Equilibrium Climate Sensitivity of each GCM used as ACCESS-ESM1-5 has
a higher ECS value than GFDL-CM4, with reefs experiencing large continuous declines under
GFDL-CM4. These large declines are likely due to the high peak thermal stress levels above
10°C-weeks experienced in the first ten years of the timeseries under GFDL-CM4.

>>>>

: Table 1: Information for each GCM used in this investigation including ECS value,
interpreted relative severity and where results are individual GCM results are displayed.
GCMs in context with assessed plausible ranges of ECS values are displayed in [@fig-ecs].
ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS values, thus
results are displayed in the main text. ECS value sources: .

@@

\[**TI:** **For Takuya to flesh out**\]

@@

Under all GCMs most reefs are projected to suffer substantial declines in coral cover
relative to 2025 levels. NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover
maintenance into the future. Differences between low, medium and high reef clusters in cover
timeseries are most notable under these two GCMs. Maintainance of coral cover into the
future is not clearly linked to the Equilibrium Climate Sensitivity of each GCM used as
ACCESS-ESM1-5 has a higher ECS value than GFDL-CM4, with reefs experiencing large continuous
declines under GFDL-CM4. These large declines are likely due to the high peak thermal stress
levels above 10°C-weeks experienced in the first ten years of the timeseries under GFDL-CM4.
